LAGOS lake depth

### 2019-10-14 lagos_depth.Rmd
towards workflow fig

hypso_ct <- read.csv("data/ct_hypso.csv", stringsAsFactors = FALSE) %>%
  select(-n) %>% group_by(id) %>%  add_tally() %>% ungroup() %>%
  dplyr::filter(n > 3) %>%
  filter(!str_detect(id, "Cove"))
hypso_mn <- read.csv("data/mn_hypso.csv", stringsAsFactors = FALSE)
```

@@

# use plotly::ggplotly to select specific lakes
# dplyr::filter(hypso_ct, id == "lake_saltonstall") # super deep
# "pickerel_lake" # convex
# "long_pond" # concave

rsub1 <- raster::raster("data/ct_bathy/pickerel_lake.tif")
rsub2 <- raster::raster("data/ct_bathy/long_pond.tif")
names(rsub1) <- "layer"
names(rsub2) <- "layer"

@@

```{r get-hypso-normalized, eval=TRUE, fig.height = 4}
cowplot::plot_grid(
  ggplot(data = hypso, aes(x = radius_percent, y = depth_percent)) +
    geom_point(aes(color = type)) + geom_line(aes(color = type)) +
    xlab("Radius distance (percent)") + ylab("Depth (percent)") + 
    ylim(c(100, 0)) +  theme(legend.position = "none"),
ggplot(data = hypso, aes(x = area_percent, y = depth_percent)) +
  geom_point(aes(color = type)) + geom_line(aes(color = type)) +
  xlab("Area > depth (percent)") + ylab("Depth (percent)") +
    ylim(c(100, 0)),
rel_widths = c(0.6, 1)
)

@@

>>>>

hypso_ct <- read.csv("data/ct_hypso.csv", stringsAsFactors = FALSE) %>%
  select(-n) %>% group_by(llid, WBNAME) %>%  
  add_tally() %>% ungroup() %>%
  dplyr::filter(n > 3) %>%
  filter(!str_detect(WBNAME, "Cove"))
hypso_mn <- read.csv("data/mn_hypso.csv", stringsAsFactors = FALSE)
```

@@

# use plotly::ggplotly to select specific lakes
# dplyr::filter(hypso_ct, id == "lake_saltonstall") # super deep
# "pickerel_lake" 7096 # convex
# "long_pond" 99642 # concave

# dplyr::filter(hypso_ct, 
#               str_detect(WBNAME, c("Pickerel", "Long"))) %>%
#   distinct(llid)

rsub1 <- raster::raster("data/ct_bathy/7096.tif")
rsub2 <- raster::raster("data/ct_bathy/99642.tif")
names(rsub1) <- "layer"
names(rsub2) <- "layer"

@@

```{r get-hypso-normalized, eval=TRUE, fig.height = 4}
gg_radius_normal <- ggplot(data = hypso, 
                           aes(x = radius_percent, y = depth_percent)) +
    geom_point(aes(color = type)) + geom_line(aes(color = type)) +
    xlab("Radius distance (percent)") + ylab("Depth (percent)") + 
    ylim(c(100, 0)) +  theme(legend.position = "none")

gg_hypso_normal <- ggplot(data = hypso, aes(x = area_percent, y = depth_percent)) +
  geom_point(aes(color = type)) + geom_line(aes(color = type)) +
  xlab("Area > depth (percent)") + ylab("Depth (percent)") +
    ylim(c(100, 0))

cowplot::plot_grid(
  gg_radius_normal, gg_hypso_normal,
rel_widths = c(0.6, 1)
)

@@

```{r workflow}
gg_radius_convex <- 
  ggplot(data = dplyr::filter(hypso, type == "convex"), 
         aes(x = radius_percent, y = depth)) +
    geom_point() + geom_line() +
    xlab("Radius distance (proportion)") + ylab("Depth") +
    scale_y_reverse()

gg_hypso_convex <- ggplot(data = dplyr::filter(hypso, type == "convex"), 
                           aes(x = area_percent, y = depth)) +
    geom_point() + geom_line() +
    xlab("Area > depth (percent)") + ylab("Depth") +
  scale_y_reverse()

cowplot::plot_grid(
  gg_convex_raster, 
  ggdraw() +
  draw_image("figures/convex-rayshader.png"),
  gg_radius_convex, 
  gg_hypso_convex, 
  ncol = 1
)
```
